Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-13 ms.tex
more text and equations

\section{Dust Emission Model}
Our model is that of FDS99, which consists of two populations of dust 
grains emitting as modified blackbodies, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

\section{Markov Chains}
As explained in $\S$ %need to label ``model'' section so i can reference it

>>>>

\section{Dust Emission Model}
\label{sec:modeling}
Our model is that of FDS99, which consists of two populations of dust 
grains emitting as modified blackbodies, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $I^{*}_{545}$, the amplitude of the SED
in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a Metropolis-Hastings 
Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $I^{*}_{545}$. To be clear, we are sampling the posterior
given by:

\begin{equation}
P(I^{*}_{545}, T_2) \propto L({I_i}|I^{*}_{545}, T_2)P(T_2)
\end{equation}

The likelihood function is given by:

Where the errors on each intensity measurement, $\sigma_{\nu}$ are given by:

In order to obtain reasonable fitting results at high latitude where the
data is noisy, we include a prior on $T_2$
